---
title: "GDD Data Documentation"
author: "Nicholas Potter"
date: "June 3, 2015"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, include = TRUE, echo = TRUE)
```

## Overview

The data are a series of non-headered, tab-delimited text files, named for example: "MIROC_rcp85_48.53125_-122.46875.txt". The data files contain the month, day, average temperature, and the accumulated GDD for several different crops. 

The application needs to load the data into a data frame based on the location selected on a map. This file documents the data and the method used as we build the application.

## Application Goals

The application should allow the user to view a map and to see GDD data based on the location that they select from the map.

## Loading and Preparing the Data

A data file is loaded by the following R code:
```{r}

# load an example data file
data <- read.table('data/MIROC_rcp85_48.53125_-122.46875.txt', sep='\t')

#column names
names(data) <- c("unknown", "month", "day", "average_temperature", "Barley", "Corn", "Oats", "SpringWheat", "WinterWheat", "Alfalfa", "Pasture", "PastureHay", "Apples", "Cherry", "Grapes", "Potatoes", "GrapeJuice")

```

